Native advertising as a content marketing strategy

### 2024-09-11 analysis/paper/paper.Rmd
los

original <- read.xlsx(here("analysis", "data", "raw_data", "native_articles.xlsx"), sheetIndex = 1) %>%
  mutate(V1 = as.numeric(V1))

variables <- read.xlsx(here("analysis", "data", "raw_data", "native_research.xlsx"), sheetIndex = 1)

dta <- merge(original %>% filter(V1 %in% variables$V1),
  variables %>% select(-c(23, 24, 25)),
  by = "V1",
  all.x = TRUE)

# Convert the 'DATE' column to Date format
dta$DATE <- as.Date(dta$DATE)

stemmed <- readRDS("C:/Users/Lukas/Dropbox/Mediatoolkit/native_token_stemm.rds")
stemmed <- readRDS("C:/Users/lukas/Dropbox/Članci/Native rad/native_token_stemm.rds")

stemmed <- stemmed %>%
  rename("wordp" = "word") %>%
  rename("word" = "transformed_column")

```
</details>

@@

# Reults and discussion

@@

IND_kable

@@

```{r echo=F, eval=T, message=F , warning= FALSE, results='hide'}
IND_kable
```

@@

reach

@@

# Create the histogram
hist(filtered_dta$REACH, 
     xlab = "Reach", 
     ylab = "Frequency", 
     main = "Reach of Portals", 
     col = "blue", 
     breaks = 50)

@@

```{r echo=F, eval=T, message=F , warning= FALSE}
# Create the 'izvori' DataFrame
izvori <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7),
  text = c(
    "No source / statement",
    "Source from the organization / company",
    "Brand ambassador",
    "Influencer / celebrity",
    "Direct user of the product or service",
    "Multiple sources",
    "Source unrelated to the product or service"
  )
)

>>>>

dta <- read.xlsx(here("analysis", "data", "raw_data", "dta.xlsx"), sheetIndex = 1) %>%
  select(REACH, INDUSTRIJA, CLICKBAIT, OPREMA, `IZVORI...IZJAVE`)
```
</details>

@@

# Results and discussion

@@

@@

```{r echo=F, eval=T, message=F , warning= FALSE}
IND_kable
```

```{r echo=F, eval=T, message=F , warning= FALSE}
ggplot(dta, aes(x = INDUSTRIJA)) +
  geom_histogram(binwidth = 1, fill = "black") +  # Reduced binwidth for thicker bars
  labs(x = "Industry", y = "Frequency", title = "Industry") +
  scale_x_continuous(breaks = pretty(dta$REACH, n = 5)) +  # Set exactly 5 breaks on x-axis
  theme_minimal()
```

```{r echo=F, eval=T, message=F , warning= FALSE}
ggplot(dta, aes(x = CLICKBAIT)) +
  geom_histogram(binwidth = 1, fill = "black") +  # Reduced binwidth for thicker bars
  labs(x = "Clickbait Type", y = "Frequency", title = "Clickbait Type") +
  scale_x_continuous(breaks = pretty(dta$REACH, n = 5)) +  # Set exactly 5 breaks on x-axis
  theme_minimal()
```

```{r echo=F, eval=T, message=F , warning= FALSE}
ggplot(dta, aes(x = OPREMA)) +
  geom_histogram(binwidth = 1, fill = "black") +  # Reduced binwidth for thicker bars
  labs(x = "Visual equipment", y = "Frequency", title = "Visual equipment") +
  scale_x_continuous(breaks = pretty(dta$REACH, n = 5)) +  # Set exactly 5 breaks on x-axis
  theme_minimal()

```{r echo=F, eval=T, message=F , warning= FALSE}
ggplot(dta, aes(x = `IZVORI...IZJAVE`)) +
  geom_histogram(binwidth = 1, fill = "black") +  # Reduced binwidth for thicker bars
  labs(x = "Source Type", y = "Frequency", title = "Source Type") +
  scale_x_continuous(breaks = pretty(dta$REACH, n = 5)) +  # Set exactly 5 breaks on x-axis
  theme_minimal()
```

@@

@@

ggplot(filtered_dta, aes(x = REACH)) +
  geom_histogram(binwidth = 300, fill = "black") +  # Reduced binwidth for thicker bars
  labs(x = "Reach", y = "Frequency", title = "Reach of Portals") +
  scale_x_continuous(breaks = pretty(filtered_dta$REACH, n = 5)) +  # Set exactly 5 breaks on x-axis
  theme_minimal()

@@

```{r komm, echo=F, eval=T, message=F , warning= FALSE}
# Create the 'izvori' DataFrame
izvori <- data.frame(
  number = c(1, 2, 3, 4, 5, 6, 7),
  text = c(
    "No source / statement",
    "Source from the organization / company",
    "Brand ambassador",
    "Influencer / celebrity",
    "Direct user of the product or service",
    "Multiple sources",
    "Source unrelated to the product or service"
  )
)
